% Grace Hechavarria — Resume (LaTeX)
% Based on Jake's Resume template structure; content from resume.md and reference PDFs in ../sample resumes/
% Compile: pdflatex Grace_Hechavarria_Resume.tex

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Grace Hechavarria} \\ \vspace{1pt}
    \small
    (786) 216-2491 $|$ \href{mailto:gracehechavarria@gmail.com}{gracehechavarria@gmail.com} $|$
    \href{https://gracie.cloud}{gracie.cloud} \\
    \href{https://www.linkedin.com/in/grace-hechavarria-a817b2209}{linkedin.com/in/grace-hechavarria} $|$
    \href{https://github.com/ghechavarria}{github.com/ghechavarria} \\
    Miami, FL $|$ English, Spanish
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Florida International University}{Miami, FL}
      {MS in Information Technology, Software Development}{Projected 2027}
    \resumeSubheading
      {Broward College}{Davie, FL}
      {BAS in Information Technology, Web Development}{2021}
    \resumeSubheading
      {Broward College}{Davie, FL}
      {AS in Information Technology, Data Support}{2018}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Analyst, ERP Programmer}{Jul. 2023 -- Present}
      {Broward College}{Davie, FL}
      \resumeItemListStart
        \resumeItem{Develops, maintains, troubleshoots, and enhances ERP systems supporting academic and administrative operations using Natural 9.1, SQL, and JavaScript.}
        \resumeItem{Collaborates with programmers and analysts to resolve issues, improve features, and support reliable institutional tools.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Developer}{Oct. 2024 -- Present}
      {Broward College}{Davie, FL}
      \resumeItemListStart
        \resumeItem{Serves in a temporary secondary role supporting implementation of Broward College's new Student Information System.}
        \resumeItem{Translates technical updates, documents changes, and helps staff and students use new SIS tools effectively.}
      \resumeItemListEnd

    \resumeSubheading
      {Administrative Specialist, Computer Lab Assistant}{2019 -- 2021}
      {Broward College}{Davie, FL}
      \resumeItemListStart
        \resumeItem{Assisted students with computer science assignments, Microsoft Office, and programming coursework across HTML5, CSS, JavaScript, jQuery, SQL, PHP, Java, and Python.}
        \resumeItem{Supported the CSIT department lab by troubleshooting student questions and reinforcing technical concepts through one-on-one assistance.}
      \resumeItemListEnd

    \resumeSubheading
      {Volunteer Software Development Intern}{2019 -- 2020}
      {Broward College}{Davie, FL}
      \resumeItemListStart
        \resumeItem{Planned and developed a WordPress plugin for the CSIT Broward College website.}
        \resumeItem{Enhanced the Broward College Announcements Plugin for student D2L announcements and CSIT web pages.}
      \resumeItemListEnd

    \resumeSubheading
      {Augmented Reality Software Engineer}{2016 -- 2019}
      {3D HoloGroup}{Miami, FL}
      \resumeItemListStart
        \resumeItem{Built immersive software experiences, developing hands-on experience with interactive technology and application development.}
      \resumeItemListEnd

    \resumeSubheading
      {Database Designer Intern}{May -- Aug.\ 2016}
      {Code Explorers}{Davie, FL}
      \resumeItemListStart
        \resumeItem{Converted unstructured data to structured files for database implementation.}
        \resumeItem{Authored a Functional Requirements Document and created logical and conceptual ER models.}
        \resumeItem{Delivered MySQL code for a secure database tracking teacher comments, grades, classes, locations, and students.}
      \resumeItemListEnd

    \resumeSubheading
      {Payroll Administrator}{May -- Aug.\ 2015}
      {Power UP Personnel Services Inc.}{Medley, FL}
      \resumeItemListStart
        \resumeItem{Processed weekly payroll for an average of 85 employees and maintained personnel files.}
        \resumeItem{Entered pay rates, hours worked, and direct deposit information into the payroll register and employee database.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Organizer}{2020 -- 2025}
      {PlutoHacks, Broward College}{Davie, FL}
      \resumeItemListStart
        \resumeItem{Helped organize Broward College's annual 24-hour hackathon, supporting logistics, mentorship, and participant experience.}
        \resumeItem{Contributed to entire event planning and execution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Mooric ERP} $|$ \emph{React, TypeScript, Vite, Tailwind CSS, Framer Motion}}{}
      \resumeItemListStart
        \resumeItem{Business ERP platform website with clear product messaging and a polished client-facing experience (\href{https://mooricerp.com}{mooricerp.com}).}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Power UP Personnel} $|$ \emph{React, TypeScript, Vite, React Router, Leaflet}}{}
      \resumeItemListStart
        \resumeItem{Staffing and recruiting site built to present services clearly and support lead generation (\href{https://poweruppersonnel.com}{poweruppersonnel.com}).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Hackathons}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{ShellHacks 2023 --- Themis} $|$ \emph{Winner} $|$ HTML, CSS, JavaScript, PHP, Python, Google Cloud Vision}{}
      \resumeItemListStart
        \resumeItem{Phishing defense tool that detects AI-generated text, logos, and suspicious email language (\href{https://themis-vision.netlify.app}{themis-vision.netlify.app}).}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{ShellHacks 2021 --- Local Coin} $|$ \emph{Submitted} $|$ Kotlin, Android Studio, Coin Routes API, Figma}{}
      \resumeItemListStart
        \resumeItem{Mobile app helping newcomers understand, manage, and track cryptocurrency portfolios in one place.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{BrickHack 7 --- Theft Me} $|$ \emph{Submitted} $|$ Unity, C\#, SteamVR}{}
      \resumeItemListStart
        \resumeItem{Identity-theft game where players impersonate someone based on wallet contents and belongings.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Technica 2020 --- BeBrave} $|$ \emph{Winner} $|$ HTML5, CSS3, JavaScript, Illustrator}{}
      \resumeItemListStart
        \resumeItem{Interactive bullying-awareness scenarios for younger students (\href{https://bebrave.space}{bebrave.space}).}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Silly Hacks 2020 --- Mathwae} $|$ \emph{Winner} $|$ Python, Flask, JavaScript, Kintone}{}
      \resumeItemListStart
        \resumeItem{Mathway.com lookalike that returns intentionally incorrect answers to discourage academic dishonesty.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Silly Hacks 2020 --- Whack-a-Jerge} $|$ \emph{Submitted} $|$ Unity}{}
      \resumeItemListStart
        \resumeItem{Stress-relief whack-a-mole game built to release bottled-up frustration.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{ShellHacks 2020 --- Art Tunes} $|$ \emph{Submitted} $|$ HTML5, CSS, JavaScript, PHP}{}
      \resumeItemListStart
        \resumeItem{Web app that converts images into sound so blind users can experience art (\href{https://arttunes.online}{arttunes.online}).}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{PlutoHacks 2019} $|$ \emph{Winner}}{}
      \resumeItemListStart
        \resumeItem{Winning hackathon submission; project not listed on Devpost.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML5, CSS, JavaScript, TypeScript, Python, Java, PHP, SQL, Kotlin, C, C\#, jQuery, Git} \\
     \textbf{Frameworks \& Libraries}{: React, Vite, Tailwind CSS, Framer Motion, React Router, Leaflet, Flask, Bootstrap, WordPress} \\
     \textbf{Systems \& Tools}{: ERP support, Natural 9.1, Student Information System, MySQL, Android Studio, Unity, Google Cloud Vision, Netlify, GitHub, Microsoft Office, Figma, Adobe Illustrator, Adobe Photoshop, Clip Studio Paint, Blender} \\
     \textbf{Certifications}{: CIW JavaScript Specialist; CIW Data Analyst; CIW Database Design Specialist; CIW Web Foundations Associate; CompTIA IT Fundamentals; ICAgile Certified Professional --- Agile Product Ownership}
    }}
 \end{itemize}

\end{document}
